Data Exploration: IUCN and AquaMaps

### 2016-05-17 data_explore/data_explore.Rmd
including dpi = 600 for plotting

print(bar_taxa2)
ggsave(filename = file.path(dir_fig, 'bar_by_taxa_all.png'), 
       width = 17.8, height = 7, units = 'cm')

# taxa_df_long3 <- taxa_df %>%
#   dplyr::select(class, AquaMaps = n_am_class_solo_ass, IUCN = n_iucn_class_solo, Both = n_class_both) %>%
#   gather(dataset, n_spp, AquaMaps:Both) %>%
#   group_by(class) %>%
#   mutate(n_total = sum(n_spp, na.rm = TRUE),
#          percent = n_spp/n_total * 100)
#
# bar_taxa3 <- ggplot(taxa_df_long3, aes(x = class, y = percent, fill = dataset)) +
#   ggtheme_plot + 
#   geom_bar(stat = 'identity', alpha = .5) +
#   scale_fill_manual(values = c('AquaMaps' = 'red', 'Both' = 'mediumorchid', 'IUCN' = 'blue')) +
#   geom_text(aes(label = sprintf('n = %s', n_total), y = 3), 
#             #size = 3, 
#             angle = 90, hjust = 0, color = 'grey30') +
#   theme(axis.text.x = element_text(angle = 75, hjust = 1)) + 
#   scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) +
#   labs(# title = 'Species maps by taxonomic class, Red List-assessed only',
#        x = 'Class', 
#        y = 'Percent of assessed mapped species')
# print(bar_taxa3)
# ggsave(filename = file.path(dir_fig, 'si_bar_by_taxa_assessed.tif'), device = 'tiff', 
#        width = 17.8, height = 6, units = 'cm')

@@

ggsave(file.path(dir_fig, 'scatter_quadmap_norisk.png'),
       width = 17.8, height = 9, units = 'cm')

@@

# print(barchart_spp_gp_quads)
ggsave(plot = barchart_spp_gp_quads,
       filename = file.path(dir_fig, 'barchart_spp_gp_quads.png'),
       width = 17.8, height = 7, units = 'cm')

@@

# print(barchart_spp_risk_quads)
ggsave(plot = barchart_spp_risk_quads,
       filename = file.path(dir_fig, 'si_barchart_spp_risk_quads.tif'), device = 'tiff',
       width = 17.8, height = 4.5, units = 'cm')
ggsave(plot = barchart_spp_risk_quads,
       filename = file.path(dir_fig, 'si_barchart_spp_risk_quads.png'),
       width = 17.8, height = 4.5, units = 'cm')

>>>>

print(bar_taxa2)
ggsave(filename = file.path(dir_fig, 'bar_by_taxa_all.png'), 
       width = 17.8, height = 7, units = 'cm', dpi = 600)

# taxa_df_long3 <- taxa_df %>%
#   dplyr::select(class, AquaMaps = n_am_class_solo_ass, IUCN = n_iucn_class_solo, Both = n_class_both) %>%
#   gather(dataset, n_spp, AquaMaps:Both) %>%
#   group_by(class) %>%
#   mutate(n_total = sum(n_spp, na.rm = TRUE),
#          percent = n_spp/n_total * 100)
#
# bar_taxa3 <- ggplot(taxa_df_long3, aes(x = class, y = percent, fill = dataset)) +
#   ggtheme_plot + 
#   geom_bar(stat = 'identity', alpha = .5) +
#   scale_fill_manual(values = c('AquaMaps' = 'red', 'Both' = 'mediumorchid', 'IUCN' = 'blue')) +
#   geom_text(aes(label = sprintf('n = %s', n_total), y = 3), 
#             #size = 3, 
#             angle = 90, hjust = 0, color = 'grey30') +
#   theme(axis.text.x = element_text(angle = 75, hjust = 1)) + 
#   scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) +
#   labs(# title = 'Species maps by taxonomic class, Red List-assessed only',
#        x = 'Class', 
#        y = 'Percent of assessed mapped species')
# print(bar_taxa3)
# ggsave(filename = file.path(dir_fig, 'si_bar_by_taxa_assessed.tif'), device = 'tiff', 
#        width = 17.8, height = 6, units = 'cm', dpi = 600)

@@

ggsave(file.path(dir_fig, 'scatter_quadmap_norisk.png'),
       width = 17.8, height = 9, units = 'cm', dpi = 600)

@@

# print(barchart_spp_gp_quads)
ggsave(plot = barchart_spp_gp_quads,
       filename = file.path(dir_fig, 'barchart_spp_gp_quads.png'),
       width = 17.8, height = 7, units = 'cm', dpi = 600)

@@

# print(barchart_spp_risk_quads)
ggsave(plot = barchart_spp_risk_quads,
       filename = file.path(dir_fig, 'si_barchart_spp_risk_quads.tif'), device = 'tiff',
       width = 17.8, height = 4.5, units = 'cm', dpi = 600)
ggsave(plot = barchart_spp_risk_quads,
       filename = file.path(dir_fig, 'si_barchart_spp_risk_quads.png'),
       width = 17.8, height = 4.5, units = 'cm', dpi = 600)
